---
title: "MasterFile"
author: "Charlotte Chang"
date: "10/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

### Key git commands:

* `git status`
* `git add`
* `git diff --cached`
    + contrast against `git diff` before and after `git add`
* `git commit -m`
* `git push -u origin <BRANCHNAME>`
    + usually: `git push -u origin master`
* `git pull`
* `git unstage head`
* `git merge`

### Example exercises

* amniote? - read in a dirty version
* plot of body mass against rmax
* calculation of central tendency

```{r amniote_data_construction, include=FALSE, eval=FALSE}
source("~/GoogleDrive/Rscripts/GenFxns/amniote.R")
load("~/GoogleDrive/Rscripts/PantropSDH/rcoleIUCN.rda")

### Isolating mammalian herbivores
rcole_df$Order <- find.taxa(rcole_df$Species, level="Order")
rcole_df$Herbivory <- extract_traits(rcole_df$Species)
rcole_df$Herbivore <- ifelse(rcole_df$Herbivory > 0.9, 1, 0) # Pineda-Munoz and Alroy 
    # Subsetting to herbivores
herbivore_df <- rcole_df[which(rcole_df$Herbivore==1 & rcole_df$MassKG >= 1 & rcole_df$Order != "Primates" & rcole_df$Order != "Pilosa" & rcole_df$Order != "Rodentia"),]
herbivore_df$rMax[herbivore_df$rMax < 0.1] <- c( mean(herbivore_df$rMax[grep("Lepus",herbivore_df$Species)]),exp(-3), 0.39)

### Dirty herbivore dataset
set.seed(100)
dirtivore_df <- herbivore_df[,c(1:3,6,8)]
    # Dirty up rMax
mess_inds <- sample(1:nrow(dirtivore_df), 20, replace=F)
dirtivore_df$rMax[mess_inds] <- paste(dirtivore_df$rMax[mess_inds],"x0aso00",collapse = "")
    # Dirty up MassKG
mess_inds <- sample(1:nrow(dirtivore_df), 20, replace=F)
dirtivore_df$MassKG[mess_inds] <- paste(dirtivore_df$MassKG[mess_inds],"pewpewpew",collapse = "")

save(file="~/GoogleDrive/JobMaterials/EEB504/EEB504/GitR/dirtivore.RData", dirtivore_df)

write.csv(dirtivore_df, file="dirtivore.csv")
```

```{r dirtivore_problems}
load("dirtivore.rda")
str(herbivore_df)
str(dirtivore_df)

summary(herbivore_df$rMax)

summary(herbivore_df$MassKG)

summary(dirtivore_df$rMax)

summary(dirtivore_df$MassKG)
```

Subsequently:

* They fix breaks in code in small groups

```{r}
# Find how many are non-numeric
# Subset to the non-numerics
# Show the pattern
# gsub
# plot rmax ~ log body mass
```


* They fix a broken Rmd file to get the html to look nice


* They add tabs to the website in small groups

### Convert this into ioslides

